### 2024-08-25 paper.tex
some introduction

\section{Introduction}
We will review the definition of a Springer fiber and define, for a nilpotent \(Y \in \gl_m\), the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
For every \(n\) and every nilpotent \(Y \in \gl_m\), we will find the irreducible components of the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
Finally, we will use our results about Springer fibers at \(n\)-Slodowy slices to find the irreducible components of some other variety (which probably needs a name), and show that they all have the same dimension.

@@

\begin{lemma}\label{normalization_helper_two}
    For any \(n\) and linear \(f : \mathbb{C}^n \to \mathbb{C}\), there is a Jordan basis \(e_j\) for \(J_n\) such that there is at most one \(j\) with \(f(e_j) \neq 0\).
\end{lemma}
\begin{proof}
    Let \(e_j\) be a Jordan basis for \(J_n\).
    If \(\{j : f(e_j) \neq 0\}\) is the empty set, we are done.
    Otherwise, let \(j_0 = \min\{j : f(e_j) \neq 0\}\).
    For any Jordan basis \(f_j\) with \(j_0 = \min\{j : f(e_j) \neq 0\}\), define 
    \[S((f_j)_j) := \begin{cases}
        -1, & \{j > j_0 : f(e_j) \neq 0\} = \emptyset \\
        n - \min\{j > j_0 : f(e_j) \neq 0\}, & \textrm{otherwise}
    \end{cases}.\]
    We proceed by induction on \(S\).
    That is, let \((e_j)_j\) be a Jordan basis for \(J_n\) with \(j_0 = \min\{j : f(e_j) \neq 0\}\).
    Our inductive hypothesis is that if there exists a Jordan basis \((e_j')_j\) with \(j_0 = \min\{j : f(e_j') \neq 0\}\) and \(S((e_j')_j) < S((e_j)_j)\), then the conclusion holds.
    \par We have two cases: either \((e_j)_j\) satisfies the desired property, or not.
    If not, then let \(j_1 = \min\{j > j_0 : f(e_j) \neq 0\}\), and define a new Jordan basis \(e_j'\) as follows.
    \begin{itemize}
        \item \(e_n' := e_n - \frac{f(e_{j_1})}{f(e_{j_0})} e_{n - (j_1 - j_0)}\)
        \item For \(j < n\), \(e_j' := J_n^{n - j} e_n'\)
    \end{itemize}
    It is straightforward to check that \(j_0 = \min\{j : f(e_j) \neq 0\}\), and that \(S((e_j')_j) \leq S((e_j)_j) - 1\).
    By our inductive hypothesis, we are done.
\end{proof}

@@

Let \(\mu(I, (\rho_i))\) be the shape of the Jordan basis given in the previous lemma.
Let \(X_\mu\) be the Springer fiber at \(J(\mu)\), and let \((X_{\mu, \alpha})_{\alpha \in \mathrm{SYT}(\mu)}\) be the irreducible components.
\par Given a zero-indexed list \(L = [L_0, ..., L_{l - 1}]\), we define \(\gamma(L) = \sum_i i L_i\).
We will be interested in this thing because the dimension of \(X_\mu\) is \(\gamma([\mu_1, ..., \mu_l])\).
Let \(s\) be the function taking integer lists to lists which sorts the input in nonincreasing order.

\begin{lemma}
    \[\gamma([\mu_1, ..., \mu_l]) = \gamma([0, \lambda_1, ..., \lambda_k]) - \] 
    \[\left[\sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k})\right].\]
\end{lemma}
\begin{proof}
    Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
    Note that \(\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...]\).
    Let \(L'\) be the result of taking \(\mu\) and, for each \(x\), replacing one occurence of \(q_{i_x} + p_{i_{x + 1}}\) by \(q_{i_x} + p_{i_x}\); that is,
    \(L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}]\).
    Note that we get from \(\mu\) to \(L'\) by just moving each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
    So,
    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^r p_{i_k} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
    \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
    Now we consider how to get from \(L'\) to \(L\).
    First we shift \(q_{i_0}\) to the left by \(\#\{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}\}\) slots.
    Then we leave \(q_{i_0}\) in place and sort the rest of the list.
    This entails shifting each \(q_{i_x} + p_{i_x}\) to the left by \(\#\{i \notin I : q_{i_x} + p_{i_x} > \lambda_i \geq q_{i_x} + p_{i_{x + 1}}\}\) slots.
    Shifting \(q_{i_x} + p_{i_x}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_x} + p_{i_x})\).
    To go from \(L'\) to \(s(L')\), we can just make these swaps repeatedly.  
    So,
    \[\gamma(L) - \gamma(L') = \]
    \[\sum_{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
    \par Now,
    \begin{align*}
        \gamma(L) - \gamma(\mu) & = \\
        [\gamma(L) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
        \left[\sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k}))\right] & + \\
        \left[\sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} p_{i_k}\right] & = \\
        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_k}\}} p_{i_k} & + \\
        \sum_{k = 1}^s \sum_{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}} (\lambda_i - q_{i_k}) & = \\
        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1} + p_{i_k}} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}) & .
    \end{align*}    
\end{proof}

>>>>

\section{Introduction}
We will review the definition of a Springer fiber and define, for a nilpotent \(Y \in \gl_m\), the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
For every \(n\) and every nilpotent \(Y \in \gl_m\), we will find the irreducible components of the Springer fiber at the \(n\)-Slodowy slice at \(Y\).
Finally, we will use our results about Springer fibers at \(n\)-Slodowy slices to find the irreducible components of some other variety (which probably needs a name), and show that they all have the same dimension.
\par Let \(\mathfrak{g} = \gl_m \times \gl_{m + n}\), with \(n > 0\).
The nilpotent cone in \(\mathfrak{g}\) is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), where \(\mathcal{N}_m\) and \(\mathcal{N}_{m + n}\) are the nilpotent cones in \(\gl_m\) and \(\gl_{m + n}\) respectively.
Let \(\mathcal{B}_m\) and \(\mathcal{B}_{m + n}\) be the varieties of Borel subalgebras of \(\gl_m\) and \(\gl_n\) respectively.
The variety of Borel subalgebras of \(\mathcal{N}\) is \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\).
Let
\[\widetilde{\mathcal{N}} := \{(\mathfrak{b}, n) \in \mathcal{B} \times \mathcal{N} : n \in \mathfrak{b}\} = \]
\[\{(\mathfrak{b}_m, \mathfrak{b}_{m + n}, n_m, n_{m + n}) \in \mathcal{B}_m \times \mathcal{B}_{m + n} \times \mathcal{N}_m \times \mathcal{N}_{m + n} : n_m \in \mathfrak{b}_m, n_{m + n} \in \mathfrak{b}_{m + n}\}.\]
We have a map \(\widetilde{\mathcal{N}} \to \mathcal{N} \hookrightarrow \mathfrak{g}\) given by the Springer resolution.
\par Let \((e, h, f)\) be the principal \(\spl_2\)-triple in \(\gl_n\).
We have an embedding \(\gl_n \hookrightarrow \gl_m \times \gl_n \hookrightarrow \gl_{m + n}\).
Let \((E, H, F)\) be the \(\spl_2\)-triple in \(\gl_{m + n}\) which is the image of \((e, h, f)\) via this embedding.
Let \(S\) be the Slodowy slice \(F + \mathfrak{z}_{\gl_m}(E)\).
We have a map \(\gl_{m + n} \to \gl_m\) given by coordinate projection.
Restricting to \(S\), we obtain \(f_1 : S \to \gl_m\).
(It turns out that this map is surjective.)
Then, we obtain \(p_1 : S \to \mathfrak{g}\) by \(x \mapsto (x, f_1(x))\).
Taking the map \(p_1 : S \to \mathfrak{g}\) and the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\), we obtain a fibred product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).

@@

\begin{lemma}\label{normalization_helper_two}
    For any \(n\) and linear \(f : \mathbb{C}^n \to \mathbb{C}\), there is a Jordan basis \(e_j\) for \(J_n\) such that there is at most one \(j\) with \(f(e_j) \neq 0\).
\end{lemma}
\begin{proof}
    Let \(e_j\) be a Jordan basis for \(J_n\).
    If \(\{j : f(e_j) \neq 0\}\) is the empty set, we are done.
    Otherwise, let \(j_0 = \min\{j : f(e_j) \neq 0\}\).
    For any Jordan basis \(f_j\) with \(j_0 = \min\{j : f(e_j) \neq 0\}\), define 
    \[S((f_j)_j) := \begin{cases}
        -1, & \{j > j_0 : f(e_j) \neq 0\} = \emptyset \\
        n - \min\{j > j_0 : f(e_j) \neq 0\}, & \textrm{otherwise}
    \end{cases}.\]
    We proceed by induction on \(S\).
    That is, let \((e_j)_j\) be a Jordan basis for \(J_n\) with \(j_0 = \min\{j : f(e_j) \neq 0\}\).
    Our inductive hypothesis is that if there exists a Jordan basis \((e_j')_j\) with \(j_0 = \min\{j : f(e_j') \neq 0\}\) and \(S((e_j')_j) < S((e_j)_j)\), then the conclusion holds.
    \par We have two cases: either \((e_j)_j\) satisfies the desired property, or not.
    If not, then let \(j_1 = \min\{j > j_0 : f(e_j) \neq 0\}\), and define a new Jordan basis \(e_j'\) as follows.
    \begin{itemize}
        \item \(e_n' := e_n - \frac{f(e_{j_1})}{f(e_{j_0})} e_{n - (j_1 - j_0)}\)
        \item For \(j < n\), \(e_j' := J_n^{n - j} e_n'\)
    \end{itemize}
    It is straightforward to check that \(j_0 = \min\{j : f(e_j') \neq 0\}\), and that \(S((e_j')_j) \leq S((e_j)_j) - 1\).
    By our inductive hypothesis, we are done.
\end{proof}

@@

Let \(\mu(I, (\rho_i))\) be the shape of the Jordan basis given in the previous lemma.
Let \(X_\mu\) be the Springer fiber at \(J(\mu)\), and let \((X_{\mu, \alpha})_{\alpha \in \mathrm{SYT}(\mu)}\) be the irreducible components.
\par Given a zero-indexed list \(L = [L_0, ..., L_{l - 1}]\), we define \(\gamma(L) = \sum_i i L_i\).
We are interested in this thing because the dimension of \(X_\mu\) is \(\gamma([\mu_1, ..., \mu_l])\).

\begin{lemma}
    \[\gamma([\mu_1, ..., \mu_l]) = \gamma([0, \lambda_1, ..., \lambda_k]) - \] 
    \[\left[\sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k})\right].\]
\end{lemma}
\begin{proof}
    Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
    Note that \(\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...]\).
    Let \(L'\) be the result of taking \(\mu\) and, for each \(x\), replacing one occurence of \(q_{i_x} + p_{i_{x + 1}}\) by \(q_{i_x} + p_{i_x}\); that is,
    \(L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}]\).
    Note that we get from \(\mu\) to \(L'\) by just moving each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
    So,
    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^r p_{i_k} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
    \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
    Now we consider how to get from \(L'\) to \(L\).
    First we shift \(q_{i_0}\) to the left by \(\#\{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}\}\) slots.
    Then we leave \(q_{i_0}\) in place and sort the rest of the list.
    This entails shifting each \(q_{i_x} + p_{i_x}\) to the left by \(\#\{i \notin I : q_{i_x} + p_{i_x} > \lambda_i \geq q_{i_x} + p_{i_{x + 1}}\}\) slots.
    Shifting \(q_{i_x} + p_{i_x}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_x} + p_{i_x})\).
    To go from \(L'\) to \(L\), we can just make these swaps repeatedly.  
    So,
    \[\gamma(L) - \gamma(L') = \]
    \[\sum_{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
    \par Now,
    \begin{align*}
        \gamma(L) - \gamma(\mu) & = \\
        [\gamma(L) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
        \left[\sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k}))\right] & + \\
        \left[\sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} p_{i_k}\right] & = \\
        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_k}\}} p_{i_k} & + \\
        \sum_{k = 1}^s \sum_{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}} (\lambda_i - q_{i_k}) & = \\
        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1} + p_{i_k}} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}) & .
    \end{align*}    
\end{proof}
